Python as a machine learning language: experiences from the scikit-learn project

### 2013-04-29 paper.tex
popularity of scikit-learn

scikit-learn \citep{pedregosa2011} is an open source machine learning library
for the Python programming language,
intended to tie in with the set of numeric and scientific packages
centered around the NumPy and SciPy libraries
\Citep{vanderwalt2011, varoquaux2013scipy}.
It is a library, rather than a novel (domain-specific) programming language,
intended to be called from Python programs;
at present, it offers no command line interface or GUI.

>>>>

% XXX the following is more of a general introduction than a project vision
scikit-learn \citep{pedregosa2011} is an open source machine learning library
for the Python programming language,
intended to tie in with the set of numeric and scientific packages
centered around the NumPy and SciPy libraries
\Citep{vanderwalt2011, varoquaux2013scipy}.
It is a library, rather than a novel (domain-specific) programming language,
intended to be called from Python programs;
at present, it offers no command line interface or GUI.

The scikit-learn project started in 2009 and has since been developed
by a team largely consisting of scientists
(both from computer science and other fields).
Its popularity can be gauged from various sources:
% TODO: list volume on the mailing list, number of contributors,
% number of issues opened and closed, number of surveys filled in.
at the time of writing,
the popular programmer's Q~\&{}A site StackOverflow\footnote{
  \url{http://stackoverflow.com/questions/tagged/scikit-learn}}
% update the following figure when paper is finalized
lists, at the time of writing, 322 scikit-learn-related questions.
